### 2015-02-11 fundamentals/intro.tex
lcoe should not be repeated

As nuclear power expands, technical, economic, political, and environmental
analyses of nuclear fuel cycles by simulators increases in importance. The
merit of advanced nuclear technologies and the fuel cycles they comprise is
shaped by myriad physical, nuclear, chemical, industrial, and political
factors. Nuclear fuel cycle simulators must therefore couple complex models of
nuclear process physics, facility deployment, and material routing.  However,
current fuel cycle simulators rely on closed platforms and inflexible
architectures which exhibit three main failure modes. First, they discourage
targeted contribution and collaboration among experts. Next, they hobble
efforts to directly compare modeling methodologies. Finally, they
over-specialize, rendering most tools applicable to only a subset of desired
simulation fidelities, scales, and applications.  The \Cyclus nuclear fuel
cycle simulator framework and its modeling ecosystem incorporate modern
insights from simulation science and software architecture to solve these
problems.  These modern methods simultaneously enable more efficient, accurate,
robust, and validated analysis.

@@

Nuclear fuel cycle simulators drive \gls{RDD} by calculating `metrics',
quantitative measures of performance that can be compared among fuel cycle
options. The feasibility of the technology development and deployment
strategies which comprise a fuel cycle option, the dynamics of transitions
between fuel cycles, and many other measures of performance can be expressed in
terms of these metrics. For example, economic feasibility is often measured in
levelized cost of electricity (\gls{LCOE}), requiring calculation of lifetime
fuel costs and electricity generation, while environmental performance might be
measured by spent fuel volume, toxicity, or mined uranium.  A meta-analysis of
fuel cycle systems studies identified over two dozen unique quantitative
metrics spanning economics and cost, environmental stainability and waste
management impacts, safety, security and nonproliferation, resource adequacy
and utilization, among others. With few exceptions, these metrics are derived
from mass balances calculated by a fuel cycle simulator.
\cite{flicker_evaluation_2014}.

@@

>>>>

As nuclear power expands, technical, economic, political, and environmental
analyses of nuclear fuel cycles by simulators increases in importance. NucleThe
merit of advanced nuclear technologies and the fuel cycles they comprise is
shaped by myriad physical, nuclear, chemical, industrial, and political
factors. Nuclear fuel cycle simulators must therefore couple complex models of
nuclear process physics, facility deployment, and material routing. However,
current fuel cycle simulators rely on closed platforms and inflexible
architectures which exhibit three main failure modes. First, they discourage
targeted contribution and collaboration among experts. Next, they hobble
efforts to directly compare modeling methodologies. Finally, they
over-specialize, rendering most tools applicable to only a subset of desired
simulation fidelities, scales, and applications.  The \Cyclus nuclear fuel
cycle simulator framework and its modeling ecosystem incorporate modern
insights from simulation science and software architecture to solve these
problems.  These modern methods simultaneously enable more efficient, accurate,
robust, and validated analysis.

@@

Nuclear fuel cycle simulators drive \gls{RDD} by calculating `metrics',
quantitative measures of performance that can be compared among fuel cycle
options. The feasibility of the technology development and deployment
strategies which comprise a fuel cycle option, the dynamics of transitions
between fuel cycles, and many other measures of performance can be expressed in
terms of these metrics. For example, economic feasibility is often measured in
\gls{LCOE}, requiring calculation of lifetime
fuel costs and electricity generation, while environmental performance might be
measured by spent fuel volume, toxicity, or mined uranium.  A meta-analysis of
fuel cycle systems studies identified over two dozen unique quantitative
metrics spanning economics and cost, environmental stainability and waste
management impacts, safety, security and nonproliferation, resource adequacy
and utilization, among others. With few exceptions, these metrics are derived
from mass balances calculated by a fuel cycle simulator.
\cite{flicker_evaluation_2014}.

@@

\input{fcsreqs}
